Manuscript title here

### 2021-04-18 doc/ms/ms.Rmd
commit to fix f'in Dropbox sync/backup issues. Hopefully doesn't mess it up further.

```{r import general objects, echo=FALSE, warning=FALSE, message=FALSE}

@@

Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),2)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),2)`] to `r round((max_flux$flux_mg_m_y_mean/1000),2)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),2)`].

@@

drake::loadd(gini_analysis)
gini_summary = gini_analysis[["stream_gini_summary"]]

@@

Generally, the material fluxes within a stream were distributed unevenly among consumers, however, this varied among streams (Figure X). This was partly due to marked differences in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers. After accounting for species richness material fluxes were unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant97.5') %>% round(2)`])

>>>>

```{r import general objects, echo=FALSE, message=FALSE, warning=FALSE}

@@

Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.

@@

drake::loadd(gini_analysis)
gini_summary = gini_analysis[["stream_gini_summary"]] %>% set_names(make.names(names(.)))

@@

Generally, the material fluxes within a stream were distributed unequally among consumers, however, this varied among streams (Figure 1; Figure S1). The calculated inequality, i.e. Gini coefficient, ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1). Differences in inequality were partly attributed to consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers. Patterns of material fluxes were still unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).

```{r spp flux summaries, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(spp_rankings_summary)
spp_flux_summary = spp_rankings_summary[["prod_spp_rank"]]
select_dom = function(x){
  x= x[which(!is.na(x$taxon)),]
  x = x %>% dplyr::mutate(tot_n = max(prod_ann_rank, na.rm = TRUE))
  if(sum(x$rel_flux >= 0.15) > 1){
    y = x[which(x$rel_flux >= 0.15),]
    } else{
      y = x[which(x$prod_ann_rank >= (max(x$prod_ann_rank)-1)),]
   }
  return(y)
}

spp_dominance = spp_flux_summary %>% named_group_split(site) %>% map(.,~select_dom(.x)) %>% bind_rows(.id = 'site') %>% 
  group_by(site) %>%
  dplyr::summarise(n_dom = n(), 
                   tot_n = unique(tot_n),
                   dom_flux = 1-min(rel_flux, na.rm = TRUE), 
                   dom_spp = 1-min(rel_spp))

n_dom_min = spp_dominance %>% dplyr::slice(which.min(n_dom))
n_dom_max = spp_dominance %>% dplyr::slice(which.max(n_dom))

perc_dom_min = spp_dominance %>% dplyr::slice(which.min(dom_spp))
perc_dom_max = spp_dominance %>% dplyr::slice(which.max(dom_spp))

Unequal distributions of fluxes within streams corresponded to very different patterns in dominance of OM fluxes across streams (Figure 1a). For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively). Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblage.

## Trait distributions among sites and taxa

```{r trait summary, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(spp_rankings_summary)
pb_summ = spp_rankings_summary[["PB_spp_rank"]] %>% na.omit %>% group_by(site) %>% dplyr::summarise(across(matches("pb.*mean"), ~mean(.x,na.rm = TRUE)))

m_summ = spp_rankings_summary[["M_spp_rank"]] %>% na.omit %>% group_by(site) %>% dplyr::summarise(across(matches(".*ind_mean"), ~mean(.x,na.rm = TRUE)))

drake::loadd(skew_analysis)

pb_summ = skew_analysis[["PB_skew_summ"]]

m_summ = skew_analysis[["M_skew_summ"]]
```

The fluxes of OM were distributed differently across body sizes and turnover rates (**P:B**) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Fluxes were skewed differentially towards larger body sizes (positive skew) among streams, with skew estimates with body size (**M**) ranging from `r m_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).

When compared to random

-- mean skew with M ranged from

-- The probability of observing these values of skew with pb `r pb_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`

-- The probability of observing these values of skew with M `r m_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`

### 2021-04-18 docs/ms/ms.RMD
commit to fix f'in Dropbox sync/backup issues. Hopefully doesn't mess it up further.

```{r import general objects, echo=FALSE, warning=FALSE, message=FALSE}

source("./packages.R")

```
<!--- Title page details --->

@@

## Diet analysis

@@

We were interested in how OM fluxes were distributed (randomly vs. non-randomly) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass) across the temperature gradient. We used a permutation analyses to test for non-random patterns in OM flux with species traits. First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$). We then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:

$$Sk_{flux} = f_{Q0.75} - 2f_{Q0.5} + f_{Q0.25}/ f_{Q0.75}-f_{Q0.25}$$

where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution. To determine the probability of observing the skewness we observe in the data compared to random ordering, we constructed a distribution of skewness estimates from random species ordering while maintaining the relative distribution of OM fluxes. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore we permuted 1,000,000 random species orderings and calculating the skew in the cumulative distribution of annual OM fluxes. We then use this random distribution to estimate the probability of observing a skewness as extreme or greater.

@@

```{r load objects from cache, echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)
 drake::loadd(flux_estimates)
 energy_demand = flux_estimates[["energy_demand"]]
 comm_energy_demand_summary = energy_demand %>%
    group_by(site, boot_id) %>% 
    dplyr::summarise(flux_mg_m_y = sum(flux_mg_m_y)) %>%
    ungroup %>% group_by(site) %>%
    dplyr::summarise(across(matches('flux'), list(mean = ~mean(.x, na.rm = TRUE),
                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
  bind_rows
  min_demand = comm_energy_demand_summary %>% dplyr::slice(which.min(flux_mg_m_y_mean))
  max_demand = comm_energy_demand_summary %>% dplyr::slice(which.max(flux_mg_m_y_mean))

drake::loadd(flux_summaries)
annual_comm_flux_summary = flux_summaries[["annual_comm_flux_summary"]]
min_flux = annual_comm_flux_summary %>% dplyr::slice(which.min(flux_mg_m_y_mean))
max_flux = annual_comm_flux_summary %>% dplyr::slice(which.max(flux_mg_m_y_mean))

@@

Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),2)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),2)`] to `r round((max_flux$flux_mg_m_y_mean/1000),2)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),2)`].

```{r diet import, echo = FALSE, include = TRUE, message=FALSE, warning = FALSE}
drake::loadd(modeled_diets)
diet_predictions_site = modeled_diets[["diet_predictions"]] %>%
   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
    group_by(site, diet_item) %>%
    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))

diet_predictions_item = modeled_diets[["diet_predictions"]] %>%
   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
    group_by(diet_item) %>%
    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
```

Patterns of OM flux among streams were most closely tied to total energy demands as consumer diets exhibited high similarity among streams (Figure SX). Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% round(1)`]). Calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.

@@

```{r species richness, echo = FALSE, warning=FALSE, message=FALSE}
spp_richness = energy_demand %>% group_by(site) %>% dplyr::summarise(taxon_n = n_distinct(taxon))

drake::loadd(gini_analysis)
gini_summary = gini_analysis[["stream_gini_summary"]]

```

Generally, the material fluxes within a stream were distributed unevenly among consumers, however, this varied among streams (Figure X). This was partly due to marked differences in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers. After accounting for species richness material fluxes were unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant97.5') %>% round(2)`])

>>>>

<!--- Title page details --->

@@

## **Diet analysis**

@@

We were interested in how OM fluxes were distributed (randomly vs. non-randomly) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass) across the temperature gradient. We used a permutation analyses to test for non-random patterns in OM flux with species traits. First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and measured the asymmetry in the distribution of annual OM flux with species traits. To determine the probability of observing the empirical asymmetry we constructed a random distribution of asymmetry values. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore chose to permute estimated this by randomly ordering species 10,000,000 times and calculating the skew in the cumulative distribution of annual OM fluxes. We then use this random distribution to estimate the probability of observing

@@

```{r load objects from cache, echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)
 drake::loadd(flux_estimates)
 # energy_demand = flux_estimates[["energy_demand"]]
 # comm_energy_demand_summary = energy_demand %>%
 #    bind_rows
 # min_demand = comm_energy_demand_summary %>% dplyr::slice(which.min())
drake::loadd(flux_summaries)
annual_comm_flux_summary = flux_summaries[["annual_comm_flux_summary"]]
min_flux = annual_comm_flux_summary %>% dplyr::slice(which.min(flux_mg_m_y_mean))
max_flux = annual_comm_flux_summary %>% dplyr::slice(which.max(flux_mg_m_y_mean))

@@

Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020]. Community energy demand varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),1)`-fold across streams () and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),2)` [`r paste0(round((min_flux$flux_mg_m_y_quant2.5/1000),2)," - ",round((min_flux$flux_mg_m_y_quant97.5/1000),2))`] to `r round((max_flux$flux_mg_m_y_mean/1000),2)`[`r paste0(round((max_flux$flux_mg_m_y_quant2.5/1000),2)," - ",round((max_flux$flux_mg_m_y_quant97.5/1000),2))`] $g AFDM m^{-2} y^{-1}$ (mean $\pm$ 95% percentile interval [PI]).

Patterns of OM flux among streams were most closely tied to total energy demands as consumer diets exhibited high similarity among streams (Figure SX). Diets composition among all streams were dominated by diatoms (X% $\pm$ XX), amorphous detritus (X% $\pm$ XX), and green algae (X% $\pm$ XX). Calculated percent similarity among streams ranged from XX to XX.

@@

Ranked
